Visualising CHD Pathway Inequalities by ethnicity - DRAFT

### 2024-04-16 draft_report.qmd
Edited text related to and removed regional and ICB versions of metrics 24a and 24b

-   Out of the 33 metrics along the CHD pathway, 11 have an index of disparity of greater than 10%.

-   In general (but not exclusively) these greater levels of disparity occur in the disease identification and secondary prevention pathway domains and consequently the outcome metrics related to deaths from CHD.
:::

>>>>

-   Out of the 33 metrics along the CHD pathway, 13 have an index of disparity of greater than 10%.

-   In general (but not exclusively) these greater levels of disparity occur in the disease identification and secondary and tertiary prevention pathway domains and consequently the outcome metrics related to deaths from CHD.
:::
